Carp\'{e} Data: Supporting Serendipitous Data Integration in Personal Information Management

### 2012-09-17 chi2012.tex
visualisation

\subsubsection{Strategies: Successive Elimination vs Tallying}
As described in Discussion later, we noticed several different strategies that people used to evalutate each candidate selection. One common strategy was \emph{successive elimination} - to look at a single dimension at a time, starting with the most important, ruling out candidates that did not meet the required minimum for that value.  However, when there is no clear ``most important'' aspect, this  ``greedy-style'' can result in suboptimal decisions.  By comparison, a different strategy, which we called \emph{tallying the pros and cons}, kept all candidates around, and counted up the advantages and disadvantages of each, potentially weighing each factor by its perceived importance.  This strategy is less vulnerable to getting stuck in local maxima than the former.

@@

>>>>

\subsection{Strategies: Successive Elimination vs Tallying}
As described in Discussion later, we noticed several different strategies that people used to evalutate each candidate selection. One common strategy was \emph{successive elimination} - to look at a single dimension at a time, starting with the most important, ruling out candidates that did not meet the required minimum for that value.  However, when there is no clear ``most important'' aspect, this  ``greedy-style'' can result in suboptimal decisions.  By comparison, a different strategy, which we called \emph{tallying the pros and cons}, kept all candidates around, and counted up the advantages and disadvantages of each, potentially weighing each factor by its perceived importance.  This strategy is less vulnerable to getting stuck in local maxima than the former.

@@

\subsection{Use of Data Integration Features}

To determine whether participants used the data integration features of DP, we looked at use of the \emph{multipath selection} and \emph{Same-As} features of the system.   Pertaining to path selection, all participants readily used the path selection process to select values.   Five participants (25\%) deliberately used multipath selection, defined as selecting more than one active path per group at the same time to display common values across heterogeneous items. (We did not count accidental use of multipath, such as happened a few times when a participant had an already active path and wanted to switch to a separate path accidentally).

Participants used the drag-and-drop \emph{Same-As} capability extensively. Sixteen (80\%) used \emph{Same-As} as least once; among these participants, they used \emph{Same-As} an average of 4.6 times per trial. We counted a single ``use'' as a single drag-and-drop of an individual item, or an entiredrag-and-drop of an entire group into another group.  (We did not differentiate enumerated value consolidation from entity consolidation, as these operations were not discernably different from the interface perspective.)

\subsection{Use of Visualisation Features}

To determine to what extent visualisation tools were used in condition A, 13 (65\%) used charting tools at least once, while 15 (75\%) used the map.  Determining the impact these had on performance, we discovered a significant interaction between the amount charting was used ($F(1,17)=3.26; p<0.10$) and maps were used ($F(1,17)=4.32; p<0.10$)  with time to complete the task.  Examining the coefficients of our ANOVA regression ($Y_0=8.91;\beta_{charts}=0.49;\beta_{maps}=-1.05$) we find that as charting weakly positively influences time taken, while maps negatively influences it.
